Transforming Optimal Tetrahelices between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix

### 2018-04-19 rfinaldoc/JMR-17-1184-text-only.tex
final2

\begin{proof}
By \cref{thm:eventhirds}, one can compute the (at most) three edge-lengths of an optimal
tetrahelix by formulae universally quantified by $n$ and $c$:
\begin{equation}
  \begin{split}
  1 = \text{rail} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - 
  \vec{H}_{general}(n+1,c,\rho,d_{\rho}),r)) || \text{ ,} \\
  \end{split}
\end{equation}
\begin{equation}
  \begin{split}  
  \text{one-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - 
   \vec{H}_{general}(n,c+1,\rho,d_{\rho},r)) || \text{\qquad and,} \\
  \end{split}  
\end{equation}  
  \begin{equation}
  \begin{split}    
  \text{two-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - 
   \vec{H}_{general}(n,c+2,\rho,d_{\rho},r)) || \text{ .}\\
  \end{split}  
\end{equation}

This syntax just represents the Euclidean distance between vertices. Thus:
\begin{equation}
%%  \text{one-hop} &= dist(\vec{H}_{general}(0,0,\rho,d_{\rho}),\vec{H}_{general}(0,1,\rho,d_{\rho},r))  \\  
%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (r\sin(0) - r\sin(\rho/3+1\cdot\frac{2\pi}{3}))^2  +
%%    (r\cos(0) - r\cos(\rho/3 + 1\cdot\frac{2\pi}{3}))^2} \\
%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (0  - r\sin(\rho/3 + \frac{2\pi}{3}))^2  +
%%    (r - r\cos(\rho/3 + \frac{2\pi}{3}))^2} \\
%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r^2\sin^2(\rho/3 + \frac{2\pi}{3})  +
%%    r^2(1 - \cos(\rho/3 + \frac{2\pi}{3}))^2} \\
  %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.
  \text{one-hop}  = \sqrt{\frac{d_{\rho}^2}{9} + r^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \text{\qquad where: \qquad}   d_{\rho}^2 = 1 - 4 r^2 (\sin( \rho / 2)^2.
\end{equation}

@@

By similar algebra and trigonometry:
\begin{equation}
  \text{two-hop}  = \sqrt{\frac{4 d_{\rho}^2}{9} +  r^2(\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \text{.}\\
\end{equation}

By definition of minimax edge length optimality \cref{eq:optdef}, we are trying to minimize:
\[
R(T(r)) = \frac{\max{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}}{\min{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}} \text{.}
\]
But since $\text{two-hop}(r) \geq \text{one-hop}(r)$, this is equivalent to:
\[
R(T(r)) =  \frac{   \max \{1,\text{two-hop}(r)\}}
      {   \min \{1,\text{one-hop}(r)\}} \text{.}
\]
This quantity will be equal to one of:
\begin{equation}
  \frac{\text{two-hop}(r)}{1},
\frac{1}{\text{one-hop}(r)},
\frac{\text{two-hop}(r)}{\text{one-hop}(r)} \text{.}
\label{eq:ratioset}
\end{equation}

We know that both one-hop($r$) and two-hop($r$) increase monotonically and continuously with increasing $r$.
By inspection, it seems likely that we will minimize this set by equating $\text{one-hop}(r)$ or $\text{two-hop}(r)$
to 1, but to be absolutely sure and to decide which one, we must examine the partial derivative of the ratio
 $\frac{\text{two-hop}(r)}{\text{one-hop}(r)}$ in this range.

>>>>

\begin{proof}
By \cref{thm:eventhirds}, one can compute the (at most) three edge-lengths of an optimal
tetrahelix by formulae universally quantified by $n$ and $c$:
\begin{equation}
  \begin{split}
  1 = \text{rail} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - 
  \vec{H}_{general}(n+1,c,\rho,d_{\rho}),r)) || \text{ ,} \\
  \end{split}
\end{equation}
\begin{equation}
  \begin{split}  
  \text{one-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - 
   \vec{H}_{general}(n,c+1,\rho,d_{\rho},r)) || \text{\qquad and,} \\
  \end{split}  
\end{equation}  
  \begin{equation}
  \begin{split}    
  \text{two-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - 
   \vec{H}_{general}(n,c+2,\rho,d_{\rho},r)) || \text{ .}\\
  \end{split}  
\end{equation}  
This syntax just represents the Euclidean distance between vertices. Thus:
\begin{equation}
%%  \text{one-hop} &= dist(\vec{H}_{general}(0,0,\rho,d_{\rho}),\vec{H}_{general}(0,1,\rho,d_{\rho},r))  \\  
%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (r\sin(0) - r\sin(\rho/3+1\cdot\frac{2\pi}{3}))^2  +
%%    (r\cos(0) - r\cos(\rho/3 + 1\cdot\frac{2\pi}{3}))^2} \\
%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (0  - r\sin(\rho/3 + \frac{2\pi}{3}))^2  +
%%    (r - r\cos(\rho/3 + \frac{2\pi}{3}))^2} \\
%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r^2\sin^2(\rho/3 + \frac{2\pi}{3})  +
%%    r^2(1 - \cos(\rho/3 + \frac{2\pi}{3}))^2} \\
  %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.
  \text{one-hop}  = \sqrt{\frac{d_{\rho}^2}{9} + r^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \text{\qquad where: \qquad}   d_{\rho}^2 = 1 - 4 r^2 (\sin( \rho / 2)^2.
\end{equation}

@@

By similar algebra and trigonometry:
\begin{equation}
  \text{two-hop}  = \sqrt{\frac{4 d_{\rho}^2}{9} +  r^2(\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \text{.}\\
\end{equation}
By definition of minimax edge length optimality \cref{eq:optdef}, we are trying to minimize:
\[
R(T(r)) = \frac{\max{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}}{\min{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}} \text{.}
\]
But since $\text{two-hop}(r) \geq \text{one-hop}(r)$, this is equivalent to:
\[
R(T(r)) =  \frac{   \max \{1,\text{two-hop}(r)\}}
      {   \min \{1,\text{one-hop}(r)\}} \text{.}
\]
This quantity will be equal to one of:
\begin{equation}
  \frac{\text{two-hop}(r)}{1},
\frac{1}{\text{one-hop}(r)},
\frac{\text{two-hop}(r)}{\text{one-hop}(r)} \text{.}
\label{eq:ratioset}
\end{equation}
We know that both one-hop($r$) and two-hop($r$) increase monotonically and continuously with increasing $r$.
By inspection, it seems likely that we will minimize this set by equating $\text{one-hop}(r)$ or $\text{two-hop}(r)$
to 1, but to be absolutely sure and to decide which one, we must examine the partial derivative of the ratio
 $\frac{\text{two-hop}(r)}{\text{one-hop}(r)}$ in this range.
